Rates and delay times of type Ia supernovae in the Dark Energy Survey

### 2021-03-10 draft.tex
Updates from Overleaf

% Please keep new commands to a minimum, and use \newcommand not \def to avoid
% overwriting existing commands. Example:
%\newcommand{\pcm}{\,cm$^{-2}$}	% per cm-squared

@@

% Abstract of the paper
\begin{abstract}
We use a sample of 881 photometrically classified type Ia supernovae (SNe Ia) discovered by the Dark Energy Survey (DES) in the redshift range $0.2 < z <0.6$, along with 40415 field galaxies to calculate the rate of SNe Ia per galaxy. We recover the established positive trend of SN Ia rate as a function of galaxy stellar mass across a broad range of scales $8.5 \leq \log(M_*/\mathrm{M}_{\odot}) \leq 11.25$. We find that the SN Ia rate increases with stellar mass roughly linearly in log space, with a slope of $0.63 \pm 0.02$, which is consistent with previous work. We use an empirical model of stellar mass assembly to estimate the average star-formation histories (SFHs) of galaxies across the stellar mass range of our measurement. Combining the modelled SFHs with the SN Ia rates to estimate constraints on the SN Ia delay time distribution (DTD), we find the data are fit well by a power-law DTD with index $\beta = -1.14 \pm 0.05$ and normalisation $A = 2.1 \pm0.05 \times 10^{-13}~\mathrm{SNe}~{\mathrm{M}_{\odot}}^{-1}~\mathrm{yr}^{-1}$. Upon splitting the SN sample by properties of the light curves, we find a strong dependence on DTD slope with the SN stretch parameter, with slower-declining SNe exhibiting a steeper DTD slope. We interpret this as a result of a relationship between stretch and progenitor age, and explore the implications of the result in the context of SN Ia progenitors.
\end{abstract}

@@

The progenitors of a number of core-collapse SNe (CCSNe) have been identified in high-resolution pre-explosion images \citep{Smartt2009,Eldridge2013}, allowing detailed analysis of the latter stages of massive star evolution. However, this approach has not yet been successful in identifying a progenitor of a SN Ia (e.g. \citealt{Graur2014a,Kelly2014,Graur2019}, although see \citet{McCully2014} for evidence of a progenitor for a type Iax SN). Conversely, it has been possible to search for surviving remnants of the binary system -- main sequence stars or WDs left behind at the SN location or kicked out at high velocity \citep[e.g.][]{Schaefer2012,Ruiz-Lapuente2018,Kerzendorf2018,Kerzendorf2019}. \citet{Shen2018} discovered three high-velocity WDs consistent with models of double-detonation SNe Ia. However, without an unambiguous observation of a SN Ia progenitor system or remnant companion, there is as yet no direct evidence ruling out any progenitor channel from providing a significant contribution to the total population of SNe Ia.

@@

\citet{Childress2014} showed that the $A+B$ approximation arises as a direct consequence of the combination of a power-law DTD with the average SFHs of galaxies -- the prompt component proportional to the amount of on-going star-formation at the epoch of observation, and the tardy component caused by the fact that massive galaxies experienced high SFRs several Gyrs ago. The recent advances of integral field spectroscopy (IFS) allows for an extension of the SFHR method, by reconstructing the SFH for hundreds or thousands of local regions of each SN Ia host galaxy. Using this method, \citet{Castrillo2020} find a power-law slope of $-1.1\pm0.3$, while \citet{Chen2021} find $-1.4\pm0.3$.

The majority of observational evidence based on studies of SN Ia populations thus points towards a DD scenario for most, if not all, SNe Ia. However, finding self-consistent explosion models that recreate the observed luminosity function as well as correlations between luminosity, light curve parameters, and host galaxy properties has proven difficult. In particular, simulations based around explosions of $M_{\mathrm{Ch}}$ WDs fail to reproduce the observed relationship between SN luminosity and light curve duration as well as "peculiar" objects \citep{Sim2013,Blondin2017}. In recent years, attention directed towards explosions of sub-$M_{\mathrm{Ch}}$ WDs triggered by double detonations has led to promising results \citep[e.g.][]{Shen2017,Shen2018,Townsley2019,Gronow2020,Shen2021} although they still struggle to match observations at late times in the light curve evolution \citep{Shen2021,Gronow2021}. An additional factor in support of the double-detonation model is that the SN luminosity is related to the mass of the primary WD, which itself is likely to be related to its age (although this relation is probably complicated by other factors such as accretion rate, metallicity, and the composition of the companion), thereby providing an explanation for observed relation between light curve stretch and stellar age \citep{Rigault2013,Rigault2018,Nicolas2020}.

In this work, we combine parts of the traditional methods and derive a new measurement of the SN Ia DTD. Instead of measuring the volumetric rate of SNe Ia, we measure the rate per galaxy as a function of stellar mass, as per \citet{Sullivan2006,Smith2012}. We use the stellar mass assembly model of \citet{Childress2014} to predict the stellar age distribution of galaxies for a given stellar mass at the mean redshift of our SN sample, and then forward model the DTD by convolving it with the stellar age distribution and comparing the predicted rates to the observed rates.

In Section \ref{sec:data} we introduce our large sample of SNe Ia from the Dark Energy Survey as well as our deep sample of field galaxies. We describe our detailed handling of incompleteness in Section \ref{sec:incompleteness}. We present the SN Ia rate per galaxy in Section \ref{sec:rates}. We outline our modelling of star-formation histories and our novel measurement of the power-law DTD in Section \ref{sec:model}. In Section \ref{sec:split_x1_c} we investigate how the DTD differs among sub-populations of SNe with different light curve characteristics, in particular the stretch, and show stretch to be strongly dependent on progenitor age. We conclude in Section \ref{sec:conclusion} by discussing the implications of the result.
Where relevant, we assume a spatially flat $\Lambda$CDM cosmology with $\Omega_m = 0.3$ and $H_0 = 70 \mathrm{ km s}^{-1}\mathrm{Mpc}^{-1}$. Unless otherwise stated, we assume Gaussian measurement uncertainties quoted at the $1\sigma$ level, and we quote $1\sigma$ credible intervals on derived parameters. Magnitudes are quoted in the AB system \citep{Oke1983}.

@@

\label{sec:data}
\subsection{Dark Energy Survey supernova programme \label{subsec:des}}
The Dark Energy Survey Supernova Programme (DES-SN) is a transient survey based on five six-month seasons of observations with the Dark Energy Camera (DECam; \citealt{Flaugher2015}), designed primarily to measure the light curves of SNe Ia for use as cosmological distance indicators. Transients were detected and processed using a difference imaging program \citep{Kessler2015} and vetted using a machine learning (ML) algorithm \citep{Goldstein2015}. Spectral follow-up of live SN candidates was performed on a suite of large optical telescopes \citep{Smith2020a}, leading to the initial publication of a measurement of cosmological parameters using 207 spectroscopically confirmed SNe Ia (\citealt{DESCollaboration2018a}, and references therein). Spectroscopic redshifts for host galaxies come from the OzDES Global Redshift Catalog (GRC; \footnote{\url{https://docs.datacentral.org.au/ozdes/overview/dr2/}} \citealt{Yuan2015,Childress2017,Lidman2020}), which comprises galaxies targetted as DES-SN hosts with the OzDES programme as well as redshifts from legacy catalogues in the DES-SN fields.
\subsection{Supernovae \label{subsec:host_sample}}
\subsubsection{Photometric classification and quality cuts \label{subsubsec:sn_classify}}
With over 30,000 transients passing ML selection it was not possible to obtain spectral follow up of every object. Instead we make use of photometric classification in the form of the recurrent neural network classifier \texttt{superNNova} (SNN; \citealt{Moller2019}), mirroring the approach of \citet{Scolnic2020}. We train SNN using a large suite of simulated multi-band SN light curves. \textbf{Waiting on final sample and a few words from Maria/Anais to complete this bit.} SNe Ia are simulated based on the \texttt{SALT2} model \citep{Guy2007} trained on the Joint Lightcurve Analysis (JLA) data set \citep{Betoule2014}. Synthetic CCSNe light curves are generated from the templates of \citet{Vincenzi2019}. Given the training set of synthetic light curves, SNN is able to return a classification for observed light curves. Before classifying, we remove transients with variability in multiple seasons (likely active galactic nuclei or superluminous SNe). SNN is then run on every transient with a host galaxy redshift (see Section \ref{subsubsec:sn_hosts}). We define SNe with a threshold probability of $P(\mathrm{Ia})\geq0.5$ as photometrically classified SNe Ia, although our analysis is not sensitive to this choice, since the vast majority of SNe receive classifications close to 1 or 0 \citep{Moller2019}. The photometrically classified SNe Ia are then passed through the \texttt{SALT2} framework light curve fitter and are subject to quality cuts on the light curve width (stretch; $x_1$) and colour ($c$) parameters in an identical manner to \citet{Vincenzi2020}: $-3 \leq x_1 \leq 3$, $-0.3 \leq c \leq 0.3$. This selection helps to reduce the potential contamination from core-collapse SNe (CCSNe) and outlying thermonuclear SNe. We impose further cuts on the quality of those measured parameters, which are: the uncertainty on $x_1$: $\sigma_{x_1} <1$; the uncertainty on the date at which the light curve peaked: $\sigma_{t_{\mathrm{peak}}} <2$; the SALT2 fit probability $>0.001$. The number of SNe passing each stage of these cuts is displayed in Table 2 of \citet{Vincenzi2020} and reduces the $\sim30,000$ objects to 1604 SNe. With the addition of the photometric classifier we are left with 1441 SNe with which we proceed to inspect their host galaxies.

@@

We estimate global galaxy properties for both the SN host and field galaxies that pass the quality cuts by fitting the photometry with stellar population templates in a method outlined by \citet{Sullivan2006} and consistent to that used in previous DES-SN analyses \citep{kelsey2021,Smith2020,Wiseman2020}. For SN hosts the redshift is fixed at the spectroscopically determined value, while for field galaxies we fix it at either the spectroscopic value if one exists in the OzDES GRC, or more commonly the photometrically derived value. We use the stellar population templates of \citet{Bruzual2003} and adopt a \citet{Chabrier2003} initial mass function (IMF). The fitting procedure returns a best fitting template and corresponding stellar mass ($M_*$). Upper and lower bounds on stellar mass estimates are taken as the extrema in the model parameters that are consistent with the data (given the photometric uncertainties) according to their $\chi^2$ statistic, as per \citet{Sullivan2006}. To check that the choice of templates does not bias the result, we also fit the galaxies using the P\'EGASE.2 templates \citep{Fioc1997,LeBorgne2002} and a \citet{Kroupa2001} IMF, and find results consistent within measurement uncertainties. This is consistent with the findings of \citet{Smith2020}.

@@

Completeness I, II, and III show that for surveys with sharp, well defined magnitude limits the test statistics $T_{\mathrm{C}}$ and $T_{\mathrm{V}}$ drop sharply. The DES deep stacks present a more challenging case. They cover a wide area and are compiled from tens of separate CCDs, each with its own detection efficiency. Moreover, galaxy redshifts have been estimated using photometry only, and $K$-corrections performed using an imperfect template fit, potentially leading to large systematic and statistical fluctuations in absolute magnitudes and distance moduli. To reduce the inhomogeneity while still including  large sample of objects, we limit our sample to include only data from one deep (SN-X3) field. Fig. \ref{fig:completeness} shows the values of $T_{\mathrm{C}}$ and $T_{\mathrm{V}}$. The values of the test statistics increase with $m_{\mathrm{lim, trial}}$ until a peak, before decreasing to stable values at magnitudes far beyond the limit of the survey. The shape at brighter $m_{\mathrm{lim, trial}}$ is likely caused by incompleteness at the bright end: due to the small sky area, we simply do not probe enough volume to sample the bright end of the galaxy luminosity function well enough for the statistics to be robust. To approximate an efficiency function, we fit the peak of the statistics with a polynomial function, and then normalise by the maximum and minimum values. We then interpolate between the peak and the faint-magnitude floor to find the 50\% completeness limit at the point where the normalised value of the test statistic is 0.5. These values are consistent with the value at which 50\% of the true sources are detected but have the advantage of being derived from the data without a simulation that is based on assumptions and thus susceptible to bias.

\subsubsection{$V_{\mathrm{max}}$ correction \label{subsubsec:vmax_corr}}

@@

\begin{figure}
    \centering
    \includegraphics[width=.5\textwidth]{figs/rate_vs_mass_all.png}
    \caption{The rate per galaxy of SNe Ia as a function of stellar mass. Horizontal error bars represent the width of the stellar mass bins. Vertical error bars are estimated via a Monte-Carlo resampling of the rate given the uncertainties in stellar mass. The linear fit is based on all but the lowest and highest mass bins, and takes into account uncertainties in the rate.}%The blue lines indicate the best fitting model based on a $t^{\beta}$ power law DTD convolved with SFHs based on the \citet{Childress2014} model}
    \label{fig:rate_raw}
\end{figure}

%\begin{figure}
%    \centering
%    \includegraphics[width=.5\textwidth]{figs/rate_vs_mass_split_sfr.png}
%    \caption{The rate per galaxy of SNe Ia as a function of stellar mass for moderately and highly star-forming galaxies, as well as passive galaxies.}%The blue lines indicate the best fitting model based on a $t^{\beta}$ power law DTD convolved with SFHs based on the \citet{Childress2014} model}
%    \label{fig:rate_raw_split_sfr}
%\end{figure}
%%% MODEL %%%

\begin{figure*}
    \centering
    \includegraphics[width=\textwidth]{figs/SFHs_colour.png}
    \caption{The stellar mass assembly of the Universe as prescribed by the toy model of \citet{Childress2014}. Galaxies with high stellar mass at $z=0$ formed the majority of their stars in the distant past, while lower-mass galaxies are still actively star forming in the present day.}
    \label{fig:SFHs}
\end{figure*}

\begin{figure}
    \centering
    \includegraphics[width=.5\textwidth]{figs/CSFH_MD14.png}
    \caption{Cosmic star-formation history (CSFH) as approximated by our model (cyan curve) and as a best fit to observations \citep{Madau2014}.}%The blue lines indicate the best fitting model based on a $t^{\beta}$ power law DTD convolved with SFHs based on the \citet{Childress2014} model}
    \label{fig:csfh}
\end{figure}

@@

\begin{figure}
    \centering
    \includegraphics[width=.5\textwidth]{figs/beta_A_Qerf1.1_corner_All.png}
    \caption{Posterior distributions for DTD slope $\beta$ and normalisation $A$. Displayed point estimates represent the median of the posterior samples.%The blue lines indicate the best fitting model based on a $t^{\beta}$ power law DTD convolved with SFHs based on the \citet{Childress2014} model}
    \label{fig:corner_beta_norm}}
\end{figure}

\begin{figure}
    \centering
    \includegraphics[width=.5\textwidth]{figs/beta_A_tp_Qerf1.1_corner.png}
    \caption{Posterior distributions for DTD parameters $\beta$, $A$, and $t_{\mathrm{p}}$. We display the log of $A$ for clarity. Displayed point estimates represent the median of the posterior samples.
    %The blue lines indicate the best fitting model based on a $t^{\beta}$ power law DTD convolved with SFHs based on the \citet{Childress2014} model}
    \label{fig:corner_beta_norm_tp}}
\end{figure}

\begin{figure}
    \centering
    \includegraphics[width=.5\textwidth]{figs/rate_vs_mass_DTD_fit_beta_norm_Qerf1.1.png}
    \caption{Rate per galaxy of SNe Ia as a function of stellar mass (green points) along with the prediction from the best fitting DTD parameters $\beta$, $A$, and $t_{\mathrm{p}}$ forward modelled through Eq. \ref{eq:galaxy_rate}. Samples from the posterior distribution of the model log rate are drawn in cyan while the black dashed line is the mean of the posterior.%The blue lines indicate the best fitting model based on a $t^{\beta}$ power law DTD convolved with SFHs based on the \citet{Childress2014} model}
    \label{fig:rate_fitted}}
\end{figure}

\begin{figure}
    \centering
    \includegraphics[width=.5\textwidth]{figs/SNuM.png}
    \caption{SN Ia rate per unit stellar mass as function of galaxy stellar mass. Error bars are the same as Fig. \ref{fig:rate_raw}. SDSS data (orange squares) are taken from \citet{Graur2013}. The systematically higher SNuM in DES is caused by the higher redshift of the sample, as illustrated by the DTD model prediction (coloured curves) }%The blue lines indicate the best fitting model based on a $t^{\beta}$ power law DTD convolved with SFHs based on the \citet{Childress2014} model}
    \label{fig:snum}
\end{figure}
By binning both the SN hosts and field galaxies by their stellar mass we measure the mean SN Ia rate per galaxy as a function of stellar mass, $R_{\mathrm{G}}(M_*)$. We employ a bootstrap Monte-Carlo approach in order to estimate the uncertainty in the value of the rate in each stellar mass bin. The probability distribution function (PDF) of each galaxy's stellar mass is represented by the sum of two half Gaussian distributions to represent the asymmetric positive and negative uncertainties derived in the SED fitting stage (Section \ref{sec:data}). For each SN host and field galaxy, we take 100 samples of its stellar mass by drawing at random from its PDF. For each of the 100 samples we calculate the SN rate per galaxy in each stellar mass bin via Eq \ref{eq:rate1}, using the completeness-corrected values of $N_{\mathrm{SN}}$ and $N_{\mathrm{G}}$ from Eqs. \ref{eq:corr_SN} and \ref{eq:corr_G} respectively.

@@

As noted in \citet{Childress2014}, this toy model by construction follows several empirical relations derived from galaxy observations: model galaxies follow the SMz relation and obey quenching prescriptions motivated by observed galaxies. Here we make two further checks to validate to show that the model can be used to approximate the stellar age distribution of SN Ia host galaxies in DES.

>>>>

% Please keep new commands to a minimum, and use \newcommand not \def to avoid
% overwriting existing commands. Example:
%\newcommand{\pcm}{\,cm$^{-2}$}	% per cm-squared
\defcitealias{Childress2014}{C14}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

% Abstract of the paper
\begin{abstract}
We use a sample of 881 photometrically classified type Ia supernovae (SNe Ia) discovered by the Dark Energy Survey (DES) in the redshift range $0.2 < z <0.6$, along with 40415 field galaxies to calculate the rate of SNe Ia per galaxy. We recover the established positive trend of SN Ia rate as a function of galaxy stellar mass across a broad range of scales $8.5 \leq \log(M_*/\mathrm{M}_{\odot}) \leq 11.25$. We find that the SN Ia rate increases with stellar mass roughly linearly in log space, with a slope of $0.63 \pm 0.02$, which is consistent with previous work. We use an empirical model of stellar mass assembly to estimate the average star-formation histories (SFHs) of galaxies across the stellar mass range of our measurement. Combining the modelled SFHs with the SN Ia rates to estimate constraints on the SN Ia delay time distribution (DTD), we find the data are fit well by a power-law DTD with index $\beta = -1.14 \pm 0.05$ and normalisation $A = 2.1 \pm0.05 \times 10^{-13}~\mathrm{SNe}~{\mathrm{M}_{\odot}}^{-1}~\mathrm{yr}^{-1}$, which correspond to an overall SN Ia production efficiency $N_{\mathrm{Ia}}/M_* = 0.9~_{-0.7}^{+4.0} \times 10^{-3}~\mathrm{SNe}~\mathrm{M}_{\odot}^{-1}$. Upon splitting the SN sample by properties of the light curves, we find a strong dependence on DTD slope with the SN stretch parameter, with slower-declining SNe exhibiting a steeper DTD slope. We interpret this as a result of a relationship between stretch and progenitor age, and explore the implications of the result in the context of SN Ia progenitors.
\end{abstract}

@@

The progenitors of a number of core-collapse SNe (CCSNe) have been identified in high-resolution pre-explosion images \citep{Smartt2009,Eldridge2013}, allowing detailed analysis of the latter stages of massive star evolution. However, this approach has not yet been successful in identifying a progenitor of a SN Ia (e.g. \citealt{Graur2014a,Kelly2014,Graur2019}, although see \citet{McCully2014} for evidence of a progenitor for a type Iax SN). Conversely, it has been possible to search for surviving remnants of the binary system -- main sequence stars or WDs left behind at the SN location or kicked out at high velocity \citep[e.g.][]{Schaefer2012,Ruiz-Lapuente2018,Kerzendorf2018,Kerzendorf2019}. \citet{Shen2018} discovered three high-velocity WDs consistent with models of double-degenerate, double-detonation SNe Ia. However, without an unambiguous observation of a SN Ia progenitor system or remnant companion, there is as yet no direct evidence ruling out any progenitor channel from providing a significant contribution to the total population of SNe Ia.

@@

\citet[][hereafter C14]{Childress2014} showed that the $A+B$ approximation arises as a direct consequence of the combination of a power-law DTD with the average SFHs of galaxies -- the prompt component proportional to the amount of on-going star-formation at the epoch of observation, and the tardy component caused by the fact that massive galaxies experienced high SFRs several Gyrs ago. The recent advances of integral field spectroscopy (IFS) allows for an extension of the SFHR method, by reconstructing the SFH for hundreds or thousands of local regions of each SN Ia host galaxy. Using this method, \citet{Castrillo2020} find a power-law slope of $-1.1\pm0.3$, while \citet{Chen2021} find $-1.4\pm0.3$.

The majority of observational evidence based on studies of SN Ia populations thus points towards a DD scenario for most, if not all, SNe Ia. However, finding self-consistent progenitor and explosion models that recreate the observed luminosity function as well as correlations between luminosity, light curve parameters, and host galaxy properties has proven difficult. In particular, simulations based around explosions of $M_{\mathrm{Ch}}$ WDs (linked strongly with the SD scenario but also with many DD scenarios) find difficulty in reproducing the light curves of "normal" SNe Ia as well as "peculiar" objects (\citealt{Ropke2007,Sim2013,Blondin2017}; see \citealt{Maoz2014,Jha2019} for overviews). In recent years, attention directed towards explosions of sub-$M_{\mathrm{Ch}}$ WDs triggered by double detonations (primarily related to a DD scenario) has led to promising results \citep[e.g.][]{Shen2017,Shen2018,Townsley2019,Gronow2020,Shen2021} although they still struggle to match observations at late times in the light curve evolution \citep{Shen2021,Gronow2021}. An additional factor in support of the double-detonation model is that the SN luminosity is related to the mass of the primary WD, which itself is likely to be related to its age (although this relation is probably complicated by other factors such as accretion rate, metallicity, and the composition of the companion), thereby providing an explanation for observed relation between light curve stretch and stellar age \citep{Rigault2013,Rigault2018,Rose2019,Nicolas2020}.

In this work, we combine parts of the traditional methods and derive a new measurement of the SN Ia DTD. Instead of measuring the volumetric rate of SNe Ia, we measure the rate per galaxy as a function of stellar mass, as per \citet{Sullivan2006,Smith2012}. We use the stellar mass assembly model of \citetalias{Childress2014} to predict the stellar age distribution of galaxies for a given stellar mass at the mean redshift of our SN sample, and then forward model the DTD by convolving it with the stellar age distribution and comparing the predicted rates to the observed rates.

In Section \ref{sec:data} we introduce our large sample of SNe Ia from the Dark Energy Survey (DES) as well as our deep sample of field galaxies that provide an effectively complete control sample from which to measure the rate. We describe our detailed handling of SN and galaxy incompleteness in Section \ref{sec:incompleteness}. We present the SN Ia rate per galaxy in Section \ref{sec:rates} and show that it is consistent with previous works. We outline our modelling of star-formation histories and our novel measurement of the power-law DTD in Section \ref{sec:model}. In Section \ref{sec:split_x1_c} we investigate how the DTD differs among sub-populations of SNe with different light curve characteristics, in particular the stretch, and show stretch to be strongly dependent on progenitor age. We conclude in Section \ref{sec:conclusion} by discussing the implications of the results.
Where relevant, we assume a spatially flat $\Lambda$CDM cosmology with $\Omega_m = 0.3$ and $H_0 = 70 \mathrm{ km s}^{-1}\mathrm{Mpc}^{-1}$. Unless otherwise stated, we assume Gaussian measurement uncertainties quoted at the $1\sigma$ level, and we quote the posterior median and $1\sigma$ credible intervals on derived parameters. Magnitudes are quoted in the AB system \citep{Oke1983}.

@@

\label{sec:data}
\subsection{Dark Energy Survey supernova programme \label{subsec:des}}
The Dark Energy Survey Supernova Programme (DES-SN) is a transient survey based on five six-month seasons of observations with the Dark Energy Camera (DECam; \citealt{Flaugher2015}), designed primarily to measure the light curves of SNe Ia for use as cosmological distance indicators. Transients were detected and processed using a difference imaging program \citep{Kessler2015} and vetted using a machine learning (ML) algorithm \citep{Goldstein2015}. Spectral follow-up of live SN candidates was performed on a suite of large optical telescopes \citep{Smith2020a}, leading to the initial publication of a measurement of cosmological parameters using 207 spectroscopically confirmed SNe Ia (\citealt{DESCollaboration2018a}, and references therein). Spectroscopic redshifts for host galaxies come from the OzDES Global Redshift Catalog (GRC; \footnote{\url{https://docs.datacentral.org.au/ozdes/overview/dr2/}} \citealt{Yuan2015,Childress2017,Lidman2020}), which comprises galaxies targetted as DES-SN hosts with the OzDES programme as well as redshifts from legacy catalogues in the DES-SN fields.
\subsection{Supernovae \label{subsec:host_sample}}
\subsubsection{Photometric classification and quality cuts \label{subsubsec:sn_classify}}
With over 30,000 transients passing ML selection it was not possible to obtain spectral follow up of every object. Instead we make use of photometric classification in the form of the recurrent neural network classifier \texttt{superNNova} (SNN; \citealt{Moller2019}), foloowing the approach of \citet{Scolnic2020}. A full description of the training and fitting of SNN will be presented in Vincenzi et al. \textit{in prep} and M\"{o}ller et al. \textit{in prep}; we provide a brief overview here.

We train SNN using a large suite of simulated multi-band SN light curves. SNe Ia are simulated based on the \texttt{SALT2} model \citep{Guy2007} trained on the Joint Lightcurve Analysis (JLA) data set \citep{Betoule2014}. Synthetic CCSNe light curves are generated from the templates of \citet{Vincenzi2019}. Given the training set of synthetic light curves, SNN is able to return a classification for observed light curves. Before classifying, we remove transients with variability in multiple seasons (likely active galactic nuclei or superluminous SNe). SNN is then run on every transient with a host galaxy redshift (see Section \ref{subsubsec:sn_hosts}). We define SNe with a threshold probability of $P(\mathrm{Ia})\geq0.5$ as photometrically classified SNe Ia, although our analysis is not sensitive to this choice, since the vast majority of SNe receive classifications close to 1 or 0 \citep{Moller2019}. The photometrically classified SNe Ia are then passed through the \texttt{SALT2} framework light curve fitter and are subject to quality cuts on the light curve width (stretch; $x_1$) and colour ($c$) parameters in an identical manner to \citet{Vincenzi2020}: $-3 \leq x_1 \leq 3$, $-0.3 \leq c \leq 0.3$. This selection helps to reduce the potential contamination from core-collapse SNe (CCSNe) and outlying thermonuclear SNe. We impose further cuts on the quality of those measured parameters, which are: the uncertainty on $x_1$: $\sigma_{x_1} <1$; the uncertainty on the date at which the light curve peaked: $\sigma_{t_{\mathrm{peak}}} <2$; the SALT2 fit probability $>0.01$. The number of SNe passing each stage of these cuts is displayed in Table 2 of \citet{Vincenzi2020} and reduces the $\sim30,000$ objects to 1604 SNe. With the addition of the photometric classifier we are left with 1441 SNe with which we proceed to inspect their host galaxies. While the inclusion of stringent cuts significantly reduces the size of the sample, it greatly enhances the purity and is in line with previous rates analyses of this nature \citep{Sullivan2006} as well as being consistent with other DES-SN analyses \citep[e.g.][]{Kelsey2021}.

@@

We estimate global galaxy properties for both the SN host and field galaxies that pass the quality cuts by fitting the photometry with stellar population templates in a method outlined by \citet{Sullivan2006} and consistent to that used in previous DES-SN analyses \citep{Kelsey2021,Smith2020,Wiseman2020}. For SN hosts the redshift is fixed at the spectroscopically determined value, while for field galaxies we fix it at either the spectroscopic value if one exists in the OzDES GRC, or more commonly the photometrically derived value. We use the stellar population templates of \citet{Bruzual2003} and adopt a \citet{Chabrier2003} initial mass function (IMF). The fitting procedure returns a best fitting template and corresponding stellar mass ($M_*$). Upper and lower bounds on stellar mass estimates are taken as the extrema in the model parameters that are consistent with the data (given the photometric uncertainties) according to their $\chi^2$ statistic, as per \citet{Sullivan2006}. To check that the choice of templates does not bias the result, we also fit the galaxies using the P\'EGASE.2 templates \citep{Fioc1997,LeBorgne2002} and a \citet{Kroupa2001} IMF, and find results consistent within measurement uncertainties. This is consistent with the findings of \citet{Smith2020}.

@@

Completeness I, II, and III show that for surveys with sharp, well defined magnitude limits the test statistics $T_{\mathrm{C}}$ and $T_{\mathrm{V}}$ drop sharply. The DES deep stacks present a more challenging case. They cover a wide area and are compiled from tens of separate CCDs, each with its own detection efficiency. Moreover, galaxy redshifts have been estimated using photometry only, and $K$-corrections performed using an imperfect template fit, potentially leading to large systematic and statistical fluctuations in absolute magnitudes and distance moduli. To reduce the inhomogeneity while still including  large sample of objects, we limit our sample to include only data from one deep (SN-X3) field. Fig. \ref{fig:completeness} shows the values of $T_{\mathrm{C}}$ and $T_{\mathrm{V}}$. The values of the test statistics increase with $m_{\mathrm{lim, trial}}$ until a peak, before decreasing to stable values at magnitudes far beyond the limit of the survey. The shape at brighter $m_{\mathrm{lim, trial}}$ is likely caused by incompleteness at the bright end: due to the small sky area, we simply do not probe enough volume to sample the bright end of the galaxy luminosity function well enough for the statistics to be robust. To approximate an efficiency function, we fit the peak of the statistics with a polynomial function, and then normalise by the maximum and minimum values. We then interpolate between the peak and the faint-magnitude floor to find the 50\% completeness limit at the point where the normalised value of the test statistic is 0.5. These values are consistent with the value at which 50\% of the true sources are detected but have the advantage of being derived from the data without a simulation that is based on assumptions and thus susceptible to bias.
\subsubsection{$V_{\mathrm{max}}$ correction \label{subsubsec:vmax_corr}}

@@

\begin{figure}
    \centering
    \includegraphics[width=.5\textwidth]{figs/rate_vs_mass_all.png}
    \caption{The rate per galaxy of SNe Ia as a function of stellar mass. Horizontal error bars represent the width of the stellar mass bins. Vertical error bars are estimated via a Monte-Carlo resampling of the rate given the uncertainties in stellar mass. The linear fit is based on all but the lowest and highest mass bins, and takes into account uncertainties in the rate.}%The blue lines indicate the best fitting model based on a $t^{\beta}$ power law DTD convolved with SFHs based on the \citetalias{Childress2014} model}
    \label{fig:rate_raw}
\end{figure}

%\begin{figure}
%    \centering
%    \includegraphics[width=.5\textwidth]{figs/rate_vs_mass_split_sfr.png}
%    \caption{The rate per galaxy of SNe Ia as a function of stellar mass for moderately and highly star-forming galaxies, as well as passive galaxies.}%The blue lines indicate the best fitting model based on a $t^{\beta}$ power law DTD convolved with SFHs based on the \citetalias{Childress2014} model}
%    \label{fig:rate_raw_split_sfr}
%\end{figure}
%%% MODEL %%%

\begin{figure*}
    \centering
    \includegraphics[width=\textwidth]{figs/SFHs_colour.png}
    \caption{The stellar mass assembly of the Universe as prescribed by the toy model of \citetalias{Childress2014}. Galaxies with high stellar mass at $z=0$ formed the majority of their stars in the distant past, while lower-mass galaxies are still actively star forming in the present day.}
    \label{fig:SFHs}
\end{figure*}

\begin{figure}
    \centering
    \includegraphics[width=.5\textwidth]{figs/CSFH_MD14.png}
    \caption{Cosmic star-formation history (CSFH) as approximated by our model (cyan curve) and as a best fit to observations \citep{Madau2014}.}%The blue lines indicate the best fitting model based on a $t^{\beta}$ power law DTD convolved with SFHs based on the \citetalias{Childress2014} model}
    \label{fig:csfh}
\end{figure}

@@

\begin{figure}
    \centering
    \includegraphics[width=.5\textwidth]{figs/beta_A_Qerf1.1_corner_All.png}
    \caption{Posterior distributions for DTD slope $\beta$ and normalisation $A$. Displayed point estimates represent the median of the posterior samples.%The blue lines indicate the best fitting model based on a $t^{\beta}$ power law DTD convolved with SFHs based on the \citetalias{Childress2014} model}
    \label{fig:corner_beta_norm}}
\end{figure}

\begin{figure}
    \centering
    \includegraphics[width=.5\textwidth]{figs/beta_A_tp_Qerf1.1_corner.png}
    \caption{Posterior distributions for DTD parameters $\beta$, $A$, and $t_{\mathrm{p}}$. We display the log of $A$ for clarity. Displayed point estimates represent the median of the posterior samples.
    %The blue lines indicate the best fitting model based on a $t^{\beta}$ power law DTD convolved with SFHs based on the \citetalias{Childress2014} model}
    \label{fig:corner_beta_norm_tp}}
\end{figure}

\begin{figure}
    \centering
    \includegraphics[width=.5\textwidth]{figs/rate_vs_mass_DTD_fit_beta_norm_Qerf1.1.png}
    \caption{Rate per galaxy of SNe Ia as a function of stellar mass (green points) along with the prediction from the best fitting DTD parameters $\beta$, $A$, and $t_{\mathrm{p}}$ forward modelled through Eq. \ref{eq:galaxy_rate}. Samples from the posterior distribution of the model log rate are drawn in cyan while the black dashed line is the mean of the posterior.%The blue lines indicate the best fitting model based on a $t^{\beta}$ power law DTD convolved with SFHs based on the \citetalias{Childress2014} model}
    \label{fig:rate_fitted}}
\end{figure}

\begin{figure}
    \centering
    \includegraphics[width=.5\textwidth]{figs/SNuM.png}
    \caption{SN Ia rate per unit stellar mass as function of galaxy stellar mass. Error bars are the same as Fig. \ref{fig:rate_raw}. SDSS data (orange squares) are taken from \citet{Graur2013}. The systematically higher SNuM in DES is caused by the higher redshift of the sample, as illustrated by the DTD model prediction (coloured curves) }%The blue lines indicate the best fitting model based on a $t^{\beta}$ power law DTD convolved with SFHs based on the \citetalias{Childress2014} model}
    \label{fig:snum}
\end{figure}
By binning both the SN hosts and field galaxies by their stellar mass we measure the mean SN Ia rate per galaxy as a function of stellar mass, $R_{\mathrm{G}}(M_*)$. We employ a bootstrap Monte-Carlo approach in order to estimate the uncertainty in the value of the rate in each stellar mass bin. The probability distribution function (PDF) of each galaxy's stellar mass is represented by the sum of two half Gaussian distributions to represent the asymmetric positive and negative uncertainties derived in the SED fitting stage (Section \ref{sec:data}). For each SN host and field galaxy, we take 100 samples of its stellar mass by drawing at random from its PDF. For each of the 100 samples we calculate the SN rate per galaxy in each stellar mass bin via Eq \ref{eq:rate1}, using the completeness-corrected values of $N_{\mathrm{SN}}$ and $N_{\mathrm{G}}$ from Eqs. \ref{eq:corr_SN} and \ref{eq:corr_G} respectively.

@@

As noted in \citetalias{Childress2014}, this toy model by construction follows several empirical relations derived from galaxy observations: model galaxies follow the SMz relation and obey quenching prescriptions motivated by observed galaxies. Here we make two further checks to validate to show that the model can be used to approximate the stellar age distribution of SN Ia host galaxies in DES.
